### 2016-06-16 paper/algorithms.tex
more paper edits
redoing vs qoi and vs data runs from thesis with new error breakdown

\section{Inference Algorithm and Complexity Analysis}\label{sect:alg}
%
Based on the theoretical developments in the last section, we present below a goal-oriented inference algorithm that allows one to combine models of varying fidelity, while maintaining rigorous control of QoI error.
%
\subsection{Goal Oriented Inference Algorithm}
%
Just as error estimates can be used to guide mesh-refinement \cite{BecRann01}, the error estimate (\ref{eq:finErrExp}) can be localized to give elemental contributions and used to guide the division of the domain for a mixed-fidelity model. The error estimate can be calculated again, using the mixed-fidelity model as the lower-fidelity model. This process can be repeated, successively increasing the proportion of the domain in which the high-fidelity model is used, until some threshold is reached. \red{We should include something about how to map error to elements to refine.} We present below an algorithm that accomplishes the above goals.
%
\alglanguage{pseudocode}
\begin{algorithm}[h!]
\small
\caption{An algorithm to adaptively build a mixed-fidelity model for low error in the QoI.}
\label{alg:refSeries}
\begin{algorithmic}[1]
\State{Define maximum acceptable absolute relative QoI error \texttt{errTol}}
\State{Define maximum number of adaptive iterations \texttt{maxIter}}
\Procedure{$\texttt{BuildMF}$}{HF model, LF model, \texttt{errTol}, \texttt{maxIter}}
	\State{Let the model MF$_0$ be the LF model applied everywhere in the domain.}
	\State{$i\gets0$}
	\State{Solve for stationary point $\Psi_{MF_0}$ of augmented Lagrangian $\mathcal{M}_{MF_0}$}
	\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_0}$, for

@@

	$\epsilon_0=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_0})(\Lambda_0)+\mathcal M_{HF}(\Psi_{MF_0})-\mathcal M_{MF_0}(\Psi_{MF_0})$}
	\State{Calculate QoI $I(q_{MF_0},u_{MF_0})$}
	\While{$i<$ \texttt{maxIter} and $|\epsilon_i/I(q_{MF_i},u_{MF_i})|>$ \texttt{errTol}}
		\State{\begin{varwidth}[t]{\linewidth}Localize $e_{I,i}$ and use this element-wise decomposition to guide formation \par\hskip\algorithmicindent of new mixed-fidelity model MF$_{i+1}$\end{varwidth}}
		\State{$i\gets i+1$}
		\State{Solve for stationary point $\Psi_{MF_i}$ of augmented Lagrangian $\mathcal{M}_{MF_i}$}
		\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_i}$, for

@@

Note that the QoI error adjoint problem (\ref{eq:superAdjEq}) involves linearization about $\Psi_{HF}$, which is not available, so in the case of a nonlinear goal-oriented inverse problem, the QoI error adjoint problem is approximated by linearizing about $\Psi_{LF}$ instead.

Algorithm~\ref{alg:refSeries} is applicable to a large class of models. The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, be a reduced-order model, or have a reduced parameter space. The two models could also correspond to two levels of mesh-refinement, though in this case the method described in~\cite{BecVex05} could be more efficient, since interpolation could be used to estimate $\Psi_{HF}-\Psi_{LF}$ instead. The derived error estimate is not applicable to all models, however. The two models have to be expressed in a weak form, so this cannot be applied to, for example, a model of chemical reactions using kinetic Monte Carlo. We need some degree of compatibility between the two models; namely, we assume that $\Psi_{LF}$ will be in a space admissible to $\mathcal{M}'_{HF,\Psi}$, and that the QoI functional $I$ is applicable to both $(q_{HF},u_{HF})$ and $(q_{LF},u_{LF})$.
% 
\subsection{Complexity Analysis}\label{sect:alg_complexity}
%
We now derive the computational complexity of using Algorithm~\ref{alg:refSeries} to solve an inference problem, and compare it to extant strategies. Let the state, adjoint, and parameter variables each have $N$ degrees of freedom, and assume that an `all at once' strategy is used to solve the KKT system. The cost of single linear solve with such a system is $\orderof{3N}^{\gamma}$, where $\gamma$ depends on the linear solver used~\cite{}. The cost of solving for the auxiliary variables, a linear system, is $\orderof{3N}^{\gamma}$, and the cost for computing the supplementary adjoint is $\orderof{6N}^{\gamma}$.

>>>>

\section{Inference Algorithm and Complexity Analysis}\label{sect:alg}
%
Based on the theoretical developments in the last section, we present below a goal-oriented inference algorithm that allows one to combine models of varying fidelity, while maintaining rigorous control of QoI error.
%
\subsection{Goal Oriented Inference Algorithm}
%
Just as error estimates can be used to guide mesh-refinement \cite{BecRann01}, the error estimate (\ref{eq:finErrExp}) can be localized to give elemental contributions and used to guide the division of the domain for a mixed-fidelity model. The error estimate can be calculated again, using the mixed-fidelity model as the lower-fidelity model. This process can be repeated, successively increasing the proportion of the domain in which the high-fidelity model is used, until some threshold is reached. Algorithm~\ref{alg:refSeries} describes this approach. Note that the QoI error adjoint problem (\ref{eq:superAdjEq}) involves linearization about $\Psi_{HF}$, which is not available, so in the case of a nonlinear goal-oriented inverse problem, the QoI error adjoint problem is approximated by linearizing about $\Psi_{LF}$ instead.
%
\alglanguage{pseudocode}
\begin{algorithm}[h!]
\small
\caption{An algorithm to adaptively build a mixed-fidelity model for low error in the QoI.}
\label{alg:refSeries}
\begin{algorithmic}[1]
\State{Define maximum acceptable absolute relative QoI error \texttt{errTol}}
\State{Define maximum number of adaptive iterations \texttt{maxIter}}
\Procedure{$\texttt{BuildMF}$}{HF model, LF model, \texttt{errTol}, \texttt{maxIter}}
	\State{Let the model MF$_0$ be the LF model applied everywhere in the domain.}
	\State{$i\gets0$}
	\State{Solve for stationary point $\Psi_{MF_0}$ of augmented Lagrangian $\mathcal{M}_{MF_0}$}
	\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_0}$, for

@@

	$\epsilon_0=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_0})(\Lambda_0)+\mathcal M_{HF}(\Psi_{MF_0})-\mathcal M_{MF_0}(\Psi_{MF_0})$}
	\State{Calculate QoI $I(q_{MF_0},u_{MF_0})$}
	\While{$i<$ \texttt{maxIter} and $|\epsilon_i/I(q_{MF_i},u_{MF_i})|>$ \texttt{errTol}}
		\State{\begin{varwidth}[t]{\linewidth}Localize $\epsilon_i$ and use this decomposition to guide formation of new \par\hskip\algorithmicindent mixed-fidelity model MF$_{i+1}$\end{varwidth}}
		\State{$i\gets i+1$}
		\State{Solve for stationary point $\Psi_{MF_i}$ of augmented Lagrangian $\mathcal{M}_{MF_i}$}
		\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_i}$, for

@@

Algorithm~\ref{alg:refSeries} is applicable to a large class of models. The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, be a reduced-order model, or have a reduced parameter space. The two models could also correspond to two levels of mesh-refinement, though in this case the method described in~\cite{BecVex05} could be more efficient, since interpolation could be used to estimate $\Psi_{HF}-\Psi_{LF}$ instead. The derived error estimate is not applicable to all models, however. The two models have to be expressed in a weak form, so this cannot be applied to, for example, a model of chemical reactions using kinetic Monte Carlo. We need some degree of compatibility between the two models; namely, we assume that $\Psi_{LF}$ will be in a space admissible to $\mathcal{M}'_{HF,\Psi}$, and that the QoI functional $I$ is applicable to both $(q_{HF},u_{HF})$ and $(q_{LF},u_{LF})$.
% 
\subsection{Complexity Analysis}\label{sect:alg_complexity}
%
We now derive the computational complexity of using Algorithm~\ref{alg:refSeries} to solve an inference problem, and compare it to extant strategies. Let the state, adjoint, and parameter variables each have $N$ degrees of freedom, and assume that an `all at once' strategy is used to solve the KKT system. The cost of single linear solve with such a system is $\orderof{3N}^{\gamma}$, where $\gamma$ depends on the linear solver used~\cite{}. The cost of solving for the auxiliary variables, a linear system, is $\orderof{3N}^{\gamma}$, and the cost for computing the supplementary adjoint is $\orderof{6N}^{\gamma}$. \red{Solving the supplementary adjoint can be split into two $N\times N$ systems...}

### 2016-06-16 paper/numerical_experiments.tex
redoing vs qoi and vs data runs from thesis with new error breakdown

\section{Numerical Experiments}\label{sect:numexp}
%
We now use Algorithm~\ref{alg:refSeries} to solve goal oriented inverse problems in a multi-model setting. We consider two kinds of multi-fidelity models, in a total of three experiments. In the first experiment, the high fidelity model is a convection-diffusion-reaction nonlinear model, and the low fidelity model is a linear convection-diffusion model. We examine how the element-wise distribution of the error estimate is affected by changes in sensor placement and in the QoI region. In the second experiment, the high fidelity model uses an infinite dimensional (field) representation of the inferred parameter, while the low fidelity model uses a scalar representation. \red{The third experiment has the same setting as the first one, except a highly nonlinear version of the reaction term is considered, and showcases the robustness and computatioanal cost benefits of using the adaptive algorithm.}

@@

%
\subsection{Error Estimate Localization}
%
Algorithm~\ref{alg:refSeries} does not require a particular method for localizing the error estimate. A na\"{i}ve approach would be to calculate the error contribution by a particular element $\kappa$ by simply considering all area integrals in the error estimate expression, limited to that element. While perhaps simple to compute, this method results in non-zero error contributions from elements in which the high-fidelity model is already being used, making the error decomposition more difficult to interpret.

We instead use the alternative method described in \cite{vanOpstaletal15}. For convenience of notation in this section, we drop subscripts so that $\Psi=\Psi_{LF}$, $Q=Q_{HF}$, and $U=U_{HF}$; for our numerical experiments, we have $Q_{LF}\subset Q$ and $U_{LF}=U$. We note that the error estimate in Equation \ref{eq:finErrExp} can be equivalently written as

@@

@@

can be interpreted as the error contribution from the basis function $(\varphi,\upvarphi)_i$. The basis functions with the largest error contributions are flagged, and the elements in their support are refined. Using this method, elements in which the high-fidelity model is already being used are not seen as continuing to contribute to the error in the QoI, with the possible exception of elements near the interfaces between the low-fidelity and high-fidelity regions. 

@@

The unknown parameters we wish to infer correspond to the forcing field, so that $f(q)=q$. For the low-fidelity model, the inverse problem is linear (the inferred parameters are linear in the observations). Observations consisting of the state at three points in the domain are artificially generated by running the high-fidelity model on a finer mesh with the true forcing field
%
\begin{equation}
f_{true}(x_1,x_2)=
\begin{cases}
1.0 & \textrm{if }(x_1,x_2)\in[0.125,0.375]\times[0.125,0.375] \\
0.8 & \textrm{if }(x_1,x_2)\in[2.375,2.625]\times[0.375,0.625] \\
0 & \textrm{otherwise}.
\end{cases}
\end{equation}
%
The locations of the observations and the region $\Omega_I$ over which the QoI is calculated are shown in Figure~\ref{fig:baseSetup}. Since the inverse problem is ill-posed, we use Tikhonov regularization~\cite{EngHanNeu00}; the regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}A$, where $\beta=10^{-5}$ is the regularization coefficient. 
%
\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/setup_3_3.pdf}
\caption{Locations of the observations and the QoI region.}
\label{fig:baseSetup}
\end{figure}
%

For the numerical simulations, we use the finite element method (FEM), employing a continuous Galerkin formulation with Lagrange elements. We use the \texttt{libMesh} library~\cite{libMeshPaper} for the FEM calculations. \red{The library offers easy calculation of adjoint systems, error estimates and subdomain restricted variables.}\footnote{But we don't use Libmesh's error estimates or restrict variables to subdomains...} The domain is discretized by a regular mesh of quadrilaterals, with 50 and 250 elements along the short and long boundaries, respectively, for a total of 12,500 elements, resulting in a total of 38,403 degrees of freedom. The diffusion coefficient is chosen so that the cell P\'{e}clet number never exceeds 0.1, and thus no stabilization is required.
%
%------------------------------------------------------------%
\subsubsection{Adaptive Model Refinement Results} \label{sec:cdvcdrBaseRef} 
%------------------------------------------------------------%
%
We now present the results for solving the inference problem using Algorithm~\ref{alg:refSeries}. Once the QoI error estimate is calculated using Equation (\ref{eq:finErrExp}), the error estimate is then localized to each element to give an element-wise decomposition of the error. Based on this element-wise decomposition, we increase the proportion of the domain in which the high-fidelity model is used until the estimated absolute relative error in the QoI, is less than $1\%$.

Figure~\ref{fig:baseRef} shows the element-wise decomposition of the error estimate \red{no longer constant-per-element, what exactly does this plot show?}, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated. \red{note that plots show absolute values, so valleys between lobes are actually transition between positive and negative...also note which decomp method used if comparing...}
%
\begin{figure}[h!]
\centering
  \begin{subfigure}[b]{\textwidth}
  \centering    
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_LF_divvy.pdf}
    \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_LF.png}
    \vspace{-0.5\baselineskip}
    \caption{MF$_0$ ($0\%$ HF)}
    \label{fig:baseRef0}
    \vspace{0.8\baselineskip}
  \end{subfigure}
	\begin{subfigure}[b]{\textwidth}
  \centering
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF01_divvy.pdf}
    \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_MF01.png}
    \vspace{-0.5\baselineskip}
    \caption{MF$_1$ ($5\%$ HF)}
    \vspace{0.8\baselineskip}
  \end{subfigure}
  \begin{subfigure}[b]{\textwidth}
  \centering
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF02_divvy.pdf}
    \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_MF02.png}
    \vspace{-0.5\baselineskip}
    \caption{MF$_2$ ($10\%$ HF)}
    \vspace{0.8\baselineskip}
  \end{subfigure}
\caption{Element-wise decomposition of error estimate (right) and domain division (left; low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion) for mixed-fidelity models.}
\label{fig:baseRef}
\end{figure}
%
Note that since linear nodal basis elements are used, elements in regions where the high-fidelity model is already being used do not contribute to the error estimate, except some elements near the interface, whose basis function have support in both regions.

We see that model refinement is concentrated in the QoI region, and the data point closest to the QoI. In the first elemental decomposition of the error (Figure~\ref{fig:baseRef0}), the region where the elemental error is maximum is data point one. Since the constraining model is an elliptic PDE, with a weak convection, information flow is localized, and is weakly convected from left to right. Therefore, for the calculation of the QoI, it is most important to refine the region near data point one, and the QoI region. 
We also observe that the region near the data points downstream from the QoI are not refined as much as the region immediately adjacent to the QoI. This indicates that the information from these two data points is not significant for the estimation of the QoI. \red{We should say a bit more about the refinement region here, and implications for experimental design ?}.

Figure~\ref{fig:baseErr} shows the true and estimated absolute relative errors in the QoI for the various mixed-fidelity models generated by Algorithm~\ref{alg:refSeries}. \red{It can be seen that the error estimates are close to the true error, and the error estimator has an effectivity index close to one.} We also see that the QoI error of only $1\%$ is attained with a mixed-fidelity model where the high-fidelity model is used in only about $10\%$ of the domain.
%
\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/err_est.pdf}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.}
\label{fig:baseErr}
\end{figure}
%

\red{Does it make sense to compare the breakdowns and error vs refinement of the different error localization schemes? Or is one so obviously better than the other that we don't need to show it?}

%------------------------------------------------------------%
\subsubsection{Interaction of Observations and QoI} \label{sec:qoivdata}
%------------------------------------------------------------%
%
lalala
%
\subsection{Constant vs Field Parameters}
%
\subsubsection{Problem Setup}
%
\subsubsection{Results}
%
\subsection{Convection-Diffusion(-Highly Nonlinear Reaction)}
%
\subsubsection{Results}
%
We consider the convection-diffusion-reaction term described in Section \ref{sec:cdvcdr}, with a reaction term $k_r=-616$ in the high-fidelity model. This reaction term is large enough that the Newton solver will not converge with a zero initial guess. We first solve the inverse problem with the low-fidelity model ($k_r=0$), and then use a simple continuation approach, using the solution at one value of $k_r$ as the initial guess for the next.\footnote{not arclength continuation, which is more difficult to implement, though libMesh appears to have a class for such continuation, which we can use if this seems like a viable direction} We increase the reaction term in increments of $\Delta k_r=100$, and halve the increment each time the step is too large (Newton solver does not converge at the next $k_r$ value). From $k_r=0$ to $k_r=-616$, this results in 9 continuation steps being taken.
%
\subsubsection{Computational Complexity}
%
We compare the complexity of Algorithm~\ref{alg:refSeries} and the continuation method for the high fidelity problem, in the context of the analysis developed in section~\ref{sect:alg_complexity}. For the high fidelity problem, with  with 9 continuation steps, we have $\sum\limits_{i=1}^{C} K_i=30$.

>>>>

\section{Numerical Experiments}\label{sect:numexp}
%
We now use Algorithm~\ref{alg:refSeries} to solve goal oriented inverse problems in a multi-model setting. We consider two kinds of multi-fidelity models, in a total of three experiments. In the first experiment, the high fidelity model is a convection-diffusion-reaction nonlinear model, and the low fidelity model is a linear convection-diffusion model. We examine how the localized error estimate is affected by changes in sensor placement and in the QoI region. In the second experiment, the high fidelity model uses an infinite dimensional (field) representation of the inferred parameter, while the low fidelity model uses a scalar representation. \red{The third experiment has the same setting as the first one, except a highly nonlinear version of the reaction term is considered, and showcases the robustness and computatioanal cost benefits of using the adaptive algorithm.}

@@

%
\subsection{Error Estimate Localization}
%
Algorithm~\ref{alg:refSeries} does not require a particular method for localizing the error estimate. A na\"{i}ve approach would be to write the error estimate as a sum of integrals over elements and their boundaries, and calculate the error contribution by each element as the integral over that element. While perhaps simple to compute, this method results in non-zero error contributions from elements in which the high-fidelity model is already being used, making the error decomposition more difficult to interpret.

We instead use the alternative method described in \cite{vanOpstaletal15}, decomposing the error estimate into contributions from locally supported basis functions rather than elements. For convenience of notation in this section, we drop subscripts so that $\Psi=\Psi_{LF}$, $Q=Q_{HF}$, and $U=U_{HF}$; for our numerical experiments, we have $Q_{LF}\subset Q$ and $U_{LF}=U$. We note that the error estimate in Equation \ref{eq:finErrExp} can be equivalently written as

@@

\begin{equation}\label{eq:basisblame}

@@

can be interpreted as the error contribution from the basis function $(\varphi,\upvarphi)_i$. The basis functions with the largest error contributions are flagged, and the elements in their support are refined. Using this method, elements in which the high-fidelity model is already being used are not interpreted as continuing to contribute to the error in the QoI and thus are not marked again for refinement. The only exceptions are elements near the interfaces between the low-fidelity and high-fidelity regions, as basis functions near the boundary may have their support divided between the two regions and thus have a nonzero error contribution. 

@@

The unknown parameters we wish to infer correspond to the forcing field, so that $f(q)=q$. For the low-fidelity model, the inverse problem is linear (the inferred parameters are linear in the observations). Observations consisting of the state at three points in the domain are artificially generated by running the high-fidelity model on a finer mesh with the true forcing field
%
\begin{equation}
f_{true}(x_1,x_2)=
\begin{cases}
1.0 & \textrm{if }(x_1,x_2)\in[0.125,0.375]\times[0.125,0.375] \\
0.8 & \textrm{if }(x_1,x_2)\in[2.375,2.625]\times[0.375,0.625] \\
0 & \textrm{otherwise}.
\end{cases}
\end{equation}
%
The locations of the observations and the region $\Omega_I$ over which the QoI is calculated are shown in Figure~\ref{fig:baseSetup}. Since the inverse problem is ill-posed, we use Tikhonov regularization~\cite{EngHanNeu00}; the regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}A$, where $\beta=10^{-5}$ is the regularization coefficient. 
%
\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/setup_3_3.pdf}
\caption{Locations of the observations and the QoI region. \red{Aaaah spatial coordinates are not $x$ and $y$! ($y$ is one of the auxiliary variables...)}}
\label{fig:baseSetup}
\end{figure}
%

For the numerical simulations, we use the finite element method (FEM), employing a continuous Galerkin formulation with Lagrange elements. We use the \texttt{libMesh} library~\cite{libMeshPaper} for the FEM calculations. \red{The library offers easy calculation of adjoint systems, error estimates and subdomain restricted variables.}\footnote{But we don't use Libmesh's error estimates or restrict variables to subdomains...} The domain is discretized by a regular mesh of quadrilaterals, with 50 and 250 elements along the short and long boundaries, respectively, for a total of 12,500 elements, resulting in a total of 38,403 degrees of freedom. The diffusion coefficient is chosen so that the cell P\'{e}clet number never exceeds 0.1, and thus no stabilization is required.
%
%------------------------------------------------------------%
\subsubsection{Adaptive Model Refinement Results} \label{sec:cdvcdrBaseRef} 
%------------------------------------------------------------%
%
We now present the results for solving the inference problem using Algorithm~\ref{alg:refSeries}. Once the QoI error estimate is calculated using Equation~(\ref{eq:finErrExp}), the error estimate is then decomposed into local contributions, as described in Equation~(\ref{eq:basisblame}). At each iteration, based on this decomposition, we choose the basis functions with the largest error contributions until an additional 5\% of the elements has been marked for refinement. This is repeated until the estimated absolute relative error in the QoI, is less than $1\%$.

Figure~\ref{fig:baseRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated. Each linear Langrange basis function's contribution is plotted at its nonzero node.
%
\begin{figure}[h!]
\centering
  \begin{subfigure}[b]{\textwidth}
  \centering    
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_LF_divvy.png}
    \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_LF.png}
    \vspace{-0.5\baselineskip}
    \caption{MF$_0$ ($0\%$ HF)}
    \label{fig:baseRef0}
    \vspace{0.8\baselineskip}
  \end{subfigure}
	\begin{subfigure}[b]{\textwidth}
  \centering
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF01_divvy.png}
    \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_MF01.png}
    \vspace{-0.5\baselineskip}
    \caption{MF$_1$ ($5\%$ HF)}
    \vspace{0.8\baselineskip}
  \end{subfigure}
  \begin{subfigure}[b]{\textwidth}
  \centering
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF02_divvy.png}
    \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_MF02.png}
    \vspace{-0.5\baselineskip}
    \caption{MF$_2$ ($10\%$ HF)}
    \vspace{0.8\baselineskip}
  \end{subfigure}
\caption{Local error contributions (right) and domain division (left; low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion) for mixed-fidelity models.}
\label{fig:baseRef}
\end{figure}
%
Note that the error contribution of each basis function whose support is entirely within the high-fidelity regions is zero.

We see that the largest local error contribution is concentrated in the QoI region, and the data point closest to the QoI. In the first elemental decomposition of the error (Figure~\ref{fig:baseRef0}), the region where the elemental error is maximum is the leftmost data point. Since the constraining model is an elliptic PDE, with a weak convection, information flow is localized, and is weakly convected from left to right. Therefore, for the calculation of the QoI, it is most important to refine the region near the leftmost data point, and the QoI region. After that, the error decomposition suggests refinement in regions upstream and around the middle data point, and then the rightmost data point.

Figure~\ref{fig:baseErr} shows the true and estimated absolute relative errors in the QoI for the various mixed-fidelity models generated by Algorithm~\ref{alg:refSeries}. In this case, we see that the QoI error of only $1\%$ is attained with a mixed-fidelity model where the high-fidelity model is used in only about $10\%$ of the domain. We note that there is no guarantee that either the error in the QoI or the relative error in the error estimate will decrease monotonically as more of the domain is refined.
%
\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/err_est.pdf}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.}
\label{fig:baseErr}
\end{figure}
%

%------------------------------------------------------------%
\subsubsection{Interaction of Observations and QoI} \label{sec:qoivdata}
%------------------------------------------------------------%
%
lalala
%bigger steps in 3D problem because qoi region bigger?
%usually says to refine in qoi region...but what if qoi region whole domain?
%
\subsection{Constant vs Field Parameters}
%
\subsubsection{Problem Setup}
%
\subsubsection{Results}
%
\subsection{Convection-Diffusion(-Highly Nonlinear Reaction)}
%
\subsubsection{Results}
%
We consider the convection-diffusion-reaction term described in Section \ref{sec:cdvcdr}, with a reaction term $k_r=-616$ in the high-fidelity model. This reaction term is large enough that the Newton solver will not converge with a zero initial guess. We first solve the inverse problem with the low-fidelity model ($k_r=0$), and then use a simple continuation approach, using the solution at one value of $k_r$ as the initial guess for the next.\footnote{not arclength continuation, which is more difficult to implement, though libMesh appears to have a class for such continuation, which we can use if this seems like a viable direction} We increase the reaction term in increments of $\Delta k_r=100$, and halve the increment each time the step is too large (Newton solver does not converge at the next $k_r$ value). From $k_r=0$ to $k_r=-616$, this results in 9 continuation steps being taken.
%
\subsubsection{Computational Complexity}
%
We compare the complexity of Algorithm~\ref{alg:refSeries} and the continuation method for the high fidelity problem, in the context of the analysis developed in section~\ref{sect:alg_complexity}. For the high fidelity problem, with  with 9 continuation steps, we have $\sum\limits_{i=1}^{C} K_i=30$.
